ROBUST BAYESIAN RELIABILITY FOR COMPLEX SYSTEMS UNDER PRIOR-DATA CONFLICT

### 2017-12-09 asce-revision-final.tex
Frank's revision of secs1-3

\begin{abstract}
In reliability engineering, data about failure events is often scarce.
To arrive at meaningful estimates for the reliability of a system,
it is therefore often necessary to also include expert information in the analysis,
which is possible in the Bayesian approach by using an informative prior distribution.
%
A problem called prior-data conflict then can arise:
observed data seem very surprising from the viewpoint of the prior,
i.e., information from data is in conflict with prior assumptions.
Models based on conjugate priors can be insensitive to prior-data conflict,
in the sense that the spread of the posterior distribution does not increase in case of such a conflict,
thus conveying a false sense of certainty.
%
An approach to highlight this issue is presented, by considering sets of prior distributions
to model limited knowledge on Weibull distributed component lifetimes,
treating systems with arbitrary layout using the survival signature.
This approach can be seen as a robust Bayesian procedure or imprecise probability method
that reflects surprisingly early or late component failures
by wider system reliability bounds.
\end{abstract}

@@

\section{Introduction}
\label{sec:intro}
%
In reliability engineering, a central task is to describe the reliability of a complex system.
This is usually done by determining the \emph{reliability function} $R(t)$,
in other contexts also known as the \emph{survival function},
giving the probability that the system has not failed by time $t$:
\begin{linenomath*}
\begin{align}
\Rsys(t) = P(\Tsys \geq t)\,,
\end{align}
\end{linenomath*}
where $\Tsys$ is the random variable giving the failure time of the system. %
%\footnote{}
Based on the distribution of $\Tsys$, which can also be expressed
in terms of the cumulative distribution function $F_\text{sys}(t) = 1 - \Rsys(t)$,
%the density $p_\text{sys}(t)$ or the hazard rate $\lambda_\text{sys}(t)$,
decisions about, e.g., scheduling of maintenance work can be made.

Often, there is no failure data for the system itself
(e.g., if the system is a prototype, or the system is used under unique circumstances),
but there is some information about failure times for the components the system is made of.
The proposed method allows to analyse systems of arbitrary system structures, %layout of components,
i.e., any combination and nesting of series, parallel, k-out-of-n, or bridge-type arrangements,
by use of the survival signature \cite{2012:survsign}.
In doing so, the present paper extends similar previous work
which focused on a simple parallel system with homogeneous components \cite{2015:walter}.
In this paper, we assume that components can be divided into $K$ different groups,
and components within each group $k$ ($k=1, \ldots, K$) can be assumed to be exchangeable,
i.e., to follow the same failure time distribution.
Components of group $k$ are denoted as \emph{type $k$ components},
and are assumed to be independent from components of other types.
%such that failure times of components of different types are independent.
Type $k$ component lifetimes $T_i^k$ ($i = 1, \ldots, n_k$)
are assumed as Weibull distributed with type-specific parameters,
where the shape parameter $\beta_k$ is known
and the scale parameter $\lambda_k$ is unknown.

Focusing on a running system,
we assume that observations consist solely of the failure times of components in this system up to time $\tnow$,
such that the failure times of components that have not failed by $\tnow$ are right-censored,
and calculate $\Rsys(t \mid t > \tnow) = P(\Tsys \geq t \mid t > \tnow)$,
which can be used to determine the remaining useful life of the system
(in short RUL, see, e.g., \citeNP{2014:rul-review}).
%This sparse information is complemented by expert information on component lifetimes $T_i^k$.

The Bayesian approach allows to base estimation of the component failure distributions
on both data and further knowledge not given by the data,
the latter usually provided in the form of expert knowledge.
This knowledge is encoded in form of a so-called prior distribution,
which here, as the shape parameter $\beta_k$ is assumed to be known,
is a distribution on the scale parameter $\lambda_k$. %of the component lifetime distribution.
Expert knowledge is especially important when there is very few data on the components, %(like in our scenario),
as only with its help meaningful estimates for the system reliability can be made.
%
Due to the iterative nature of the Bayesian framework,
it is also possible to use a set of posteriors based on component test data as the set of priors
instead of a purely expert-based set of priors as discussed so far.
The component test data may also contain right-censored observations,
which can be treated in the same way as those from the running system
(see Section~\ref{sec:lambdawithcens} for details).

The choice of prior distribution to encode given expert knowledge is often debatable,
and a specific choice of prior is difficult to justify.
A way to deal with this is to employ sensitivity analysis,
i.e., studying the effect of different choices of prior distribution on the quantities of interest
(in our case, the system reliability function, which, in Bayesian terms, is a posterior predictive distribution).
This idea has been explored in systematic sensitivity analysis, or robust Bayesian methods
(for an overview on this approach, see, e.g.,
\citeNP{1994:berger} or \citeNP{2000:rios}).

The work presented here can be seen as belonging to the robust Bayesian approach
since it uses sets of priors. However, our focus and interpretation is slightly different,
as we consider the result of our procedure, sets of reliability functions, as the proper result,
while a robust Bayesian would base his analyses on a single reliability function from the set
in case (s)he was able to conclude that quantities of interest are not `too sensitive' to the choice of prior.
In contrast, our viewpoint is rooted in the theory of imprecise or interval probability \cite{1991:walley,itip},
where sets of distributions are used to express the precision of probability statements themselves:
the smaller the set, the more precise the probability statement.
Indeed, the system reliability function $\Rsys(t)$ is a collection of probability statements,
and a small set for $\Rsys(t)$ will indicate that the reliability of the system can be can quantified quite precisely,
while a large set will indicate that available knowledge about $\Tsys$ is rather shaky.
%
In line with imprecise or interval probability methods, the method provides, for each $t$,
a lower reliability $\lRsys(t) = \ul{P}(T_\text{sys} \geq t)$,
and an upper reliability $\uRsys(t) = \ol{P}(T_\text{sys} \geq t)$.
Sections~\ref{sec:modforsurpr} and \ref{sec:robrel} will explain how these bounds are obtained
based on sets of prior distributions on the scale parameters of the component lifetime distributions.

The central merit of the proposed method is that it adequately reflects prior-data conflict
(see, e.g., \citeNP{2006:evans}),
i.e.\ the conflict that can arise between prior assumptions on component lifetimes
and observed behaviour of components in the system under study.
As will be shown in Section~\ref{sec:weibull}, when taking the standard choice of a conjugate prior,
prior-data conflict is ignored, as the spread of the posterior distribution does not increase in case of such a conflict,
ultimately conveying a false sense of certainty
by communicating that the reliability of a system can be quantified quite precisely when in fact it can not.
%
In contrast, the proposed method will indicate prior-data conflict by wider bounds for $\Rsys(t)$.
This behaviour is obtained by a specific choice for the set of priors (see \citeNP{Walter2009a} and \citeNP{diss} \S 3.1.4)
which leads to larger sets of posterior distributions when prior knowledge and data are in conflict
(see Section~\ref{sec:modforsurpr} for more details).
If a prior based on component test data is used,
such prior-data conflict sensitivity furthermore allows to uncover a conflict between
current observations in the running system and past observations from component tests.

The topic of prior-data conflict or agreement has of course received attention within the precise Bayesian statistics framework.
For example, \citeN{2008:bousquet} proposed a method for diagnostics of agreement or disagreement between the prior and data,
based on a ratio of Kullback-Leibler divergences.
\citeN{2012:ohagan-pericchi} propose the use of heavy-tailed distributions which,
in case of conflict between multiple sources of prior information,
typically provide more weight to one or more of these, when combined with the data,
than would happen with more commonly used prior distributions.
While such approaches have some interesting features, e.g. through the quantification of level of disagreement,
they do not resolve the fundamental issue commented on here,
namely that the end result of the Bayesian inference remains a single-valued probability
which is a weighted average of the prior and data inputs.

The paper is organized as follows.
In Section~\ref{sec:weibull}, a Bayesian analysis for Weibull component lifetimes
with fixed shape parameter is described,
illustrating the issue of prior-data conflict.
Section~\ref{sec:modforsurpr} then details the use of sets of priors
for the scale parameter $\lambda_k$ of the Weibull distribution,
showing how this highlights the prior-data conflict issue for $\lambda_k$.
Section~\ref{sec:robrel} then develops a method to calculate system reliability bounds
for a running system based on sets of priors for $\lambda_k$. 
Section~\ref{sec:elicitation} discusses elicitation,
by giving guidelines on how to choose prior parameter bounds
that reflect expert information on components.
Section~\ref{sec:examples} contains examples illustrating the merits of our method,
by studying the effect of surprisingly early or late component failures,
showing that observations in conflict to prior assumptions
indeed lead to more cautious system reliability predictions.
Section~\ref{sec:concluding} concludes the paper by summarizing results
and indicating avenues for further research.

@@

Consider a system with components of $k=1,\ldots,K$ different types;
for each type $k$, there are $n_k$ exchangeable components in the system.
For each type $k$ component, we assume for its lifetime $T_i^k$ ($i=1,\ldots,n_k$, $k = 1, \ldots, K$)
a Weibull distribution with fixed shape parameter $\beta_k > 0$,
in short $T_i^k \mid \lambda_k \sim \wei(\beta_k,\lambda_k)$,
with density and cdf%
\begin{linenomath*}
\begin{align}
\label{eq:weibulldens}
f(t_i^k \mid \lambda_k) &= \frac{\beta_k}{\lambda_k} (t_i^k)^{\beta_k-1} e^{-\frac{(t_i^k)^{\beta_k}}{\lambda_k}}\,, \\
\label{eq:weibullcdf}
F(t_i^k \mid \lambda_k) &= 1 - e^{-\frac{(t_i^k)^{\beta_k}}{\lambda_k}} = P(T_i^k \leq t_i^k \mid \lambda_k)\,,
\end{align}
\end{linenomath*}
where $\lambda_k > 0$ and $t > 0$.

The shape parameter $\beta_k$ determines whether the hazard rate is increasing ($\beta_k > 1$)
or decreasing ($\beta_k < 1$) over time.
For $\beta_k=1$, one obtains the Exponential distribution with constant hazard rate as a special case.
The value for $\beta_k$ will often be clear from practical considerations.

The scale parameter $\lambda_k$ can be interpreted through the relation
\begin{linenomath*}
\begin{align}
\E[T_i^k \mid \lambda_k] &= \lambda_k^{1/\beta_k}\, \Gamma(1 + 1/\beta_k)\,.
\label{eq:lambdainterpret}
\end{align}
\end{linenomath*}
For encoding expert knowledge about the reliability of the components,
one needs to assign a prior distribution over the scale parameter $\lambda_k$.
A convenient choice is to use the inverse Gamma distribution,
commonly parametrized in terms of the hyperparameters $a_k > 0$ and $b_k > 0$:
%Conjugate prior is $\lambda_k \sim \ig(a_k,b_k)$:
\begin{linenomath*}
\begin{align}
f(\lambda_k\mid a_k,b_k) &= \frac{(b_k)^{a_k}}{\Gamma(a_k)} \lambda_k^{-a_k -1} e^{-\frac{b_k}{\lambda_k}}
\label{eq:ig-def}
\end{align}
\end{linenomath*}
in short, $\lambda_k \mid a_k, b_k \sim \ig(a_k,b_k)$.
The inverse Gamma is convenient because it is a conjugate prior,
i.e., the posterior obtained by Bayes' rule is again inverse Gamma and thus easily tractable;
the prior parameters only need to be updated to obtain the posterior parameters.

In the standard Bayesian approach, 
one has to fix a prior by choosing values for $a_k$ and $b_k$
to encode specific prior information about component lifetimes.
In our imprecise approach, we allow instead these parameters
to vary in a set, this is advantageous also
because expert knowledge is often vague,
and it is difficult for the expert(s) to pin down precise hyperparameter values.
For the definition of the hyperparameter set,
we use however a parametrization in terms of $\nz > 1$ and $\yz > 0$ instead of $a_k$ and $b_k$,
where we drop the index $k$ for the discussion about the prior model in the following,
keeping in mind that each component type will have its own specific parameters.
We use
%\begin{linenomath*}
%\begin{align}
$\nz = a - 1$ and
%&
$\yz = b / \nz$,
%\end{align}
%\end{linenomath*}
where $\yz$ can be interpreted as the prior guess for the scale parameter $\lambda$,
as $\E[\lambda\mid\nz,\yz] = \yz$.
This parametrization also makes the nature of the combination
of prior information and data through Bayes' rule more clear:
After observing $n$ component lifetimes $\vec{t} = (t_1, \ldots, t_n)$,
the updated parameters are
\begin{linenomath*}
\begin{align}
\nn &= \nz + n\,, 
&
\yn &=  \frac{\nz \yz + \taut}{\nz + n}\,,
\label{eq:ig-update}
\end{align}
\end{linenomath*}
where $\taut = \sum_{i=1}^n (t_i)^\beta$. %
%\footnote{
We thus have
\begin{linenomath*}
\begin{align}
\lambda \mid \nz, \yz, \vec{t} \sim \ig(\nz + n + 1, \nz \yz + \taut). %}
\label{eq:ig-update-alpha}
\end{align}
\end{linenomath*}
%In terms of canonical parameters $\nkz$ and $\ykz$, we assume $\lambda_k \mid \nkz,\ykz \sim \ig(\nkz + 1, \nkz\ykz)$.
From the simple update rule \eqref{eq:ig-update}, we see that
$\yn$ is a weighted average of the prior parameter $\yz$ and the maximum likelihood (ML) estimator $\taut/n$,
with weights proportional to $\nz$ and $n$, respectively.
$\nz$ can thus be interpreted as a prior strength or pseudocount,
indicating how much our prior guess should weigh against the $n$ observations.
Furthermore, $\V[\lambda\mid\nz,\yz] = (\yz)^2 / (1 - 1/\nz)$,
so for fixed $\yz$, the higher $\nz$,
the more probability mass is concentrated around $\yz$. %$p(\lambda\mid\nz,\yz)$

However, the weighted average structure for $\yn$
is behind the problematic behaviour in case of prior-data conflict.
Assume that from expert knowledge we expect
to have a mean component lifetime of 9 weeks.
Using \eqref{eq:lambdainterpret}, with $\beta=2$ we obtain $\yz = 103.13$.
We choose $\nz = 2$, so our prior guess for the mean component lifetime
counts like having two observations with this mean.
If we now have a sample of two observations
with surprisingly early failure times $t_1 = 1$ and $t_2 = 2$,
using \eqref{eq:ig-update} we get $\nfun{2} = 4$
and $\yfun{2} = \frac{1}{4}(2 \cdot 103.13 + 1^2 + 2^2) = 52.82$,
so our posterior expectation for the scale parameter $\lambda$ is $52.82$,
equivalent to a mean component lifetime of $6.44$ weeks.
The posterior standard deviation (sd) for $\lambda$ is $60.99$.
Compared to the prior standard deviation of $145.85$,
the posterior expresses now more confidence that mean lifetimes are around $\yfun{2} = 52.82$
than the prior had about $\yz = 103.13$.
This irritating conclusion is illustrated in Figure~\ref{fig:weibull-pdc};
the posterior cdf is shifted halfway towards the values for $\lambda$
that the two observations suggest
(the ML estimator for $\lambda$ would be $2.5$),
and is steeper than the prior (so the pdf is more pointed),
thus conveying a false sense of certainty about $\lambda$.
We would obtain almost the same %values of $\nfun{2}$ and $\yfun{2}$, and so the same 
posterior distribution
if we had assumed the mean component lifetime to be 7 weeks (so $\yz = 62.39$),
and observed lifetimes $t_1 = 6$, $t_2 = 7$ in line with our expectations.
It seems unreasonable to make the same probability statements on component lifetimes in these two fundamentally different scenarios.

@@

Despite this issue of ignoring prior-data conflict,
the tractability of the update step
is a very attractive feature of the conjugate setting.
As was shown by \citeN{Walter2009a} (see also \citeNP{diss}, \S 3.1),
it is possible to retain tractability and to have a meaningful reaction to prior-data conflict
when using sets of priors generated by varying both $\nz$ and $\yz$.
Then, the magnitude of the set of posteriors,
and with it the precision of posterior probability statements,
will be sensitive to the degree of prior-data conflict,
i.e.\ leading to more cautious probability statements when prior-data conflict occurs.

Instead of a single prior guess $\yz$ for the mean component lifetimes,
we will now assume a range of prior guesses $[\yzl, \yzu]$, and also a range $[\nzl, \nzu]$ of pseudocounts,
i.e., we now consider the set of priors
\begin{linenomath*}
\begin{align}
\MZ := \{ f(\lambda\mid\nz,\yz) \mid \nz \in [\nzl, \nzu], \yz \in [\yzl, \yzu] \}
\label{eq:setofpriors}
\end{align}
\end{linenomath*}
to express our prior knowledge about component lifetimes.
Each of the priors $f(\lambda\mid\nz,\yz)$ is then updated to the posterior
$f(\lambda\mid\nz,\yz,\vec{t}) = f(\lambda\mid\nn,\yn)$
by using \eqref{eq:ig-update},
such that the set of posteriors $\MN$ can be written as
$\MN = \{ f(\lambda\mid\nn,\yn) \mid \nz \in [\nzl, \nzu], \yz \in [\yzl, \yzu] \}$.
This procedure of using Bayes' Rule element by element
is seen as self-evident in the robust Bayesian literature,
but can be formally justified as being \emph{coherent}
(a self-consistency property)
in the framework of imprecise probability, where it is known as
\emph{Generalized Bayes' Rule} \cite[\S 6.4]{1991:walley}.

Technically, it is crucial to consider a range of pseudocounts $[\nzl, \nzu]$
along with the range of prior guesses $[\yzl, \yzu]$,
as only then $\taut/n \not\in [\yzl, \yzu]$
leads to the set of posteriors being larger
and hence reflecting prior-data conflict.

Continuing the example from Section~\ref{sec:weibull} and Figure~\ref{fig:weibull-pdc},
assume now for the mean component lifetimes the range 9 to 11 weeks,
this corresponds to $[\yzl,\yzu] = [103.13, 154.06]$.
Choosing $[\nzl,\nzu] =[2, 5]$
means to value this information on mean component lifetimes as equivalent to having seen two to five observations.
Compare now the set of posteriors obtained from observing
$t_1 = 1$, $t_2 = 2$ (as before), see Figure~\ref{fig:setofpost-pdc-nopdc} (left),
and $t_1 = 10$, $t_2 = 11$, see Figure~\ref{fig:setofpost-pdc-nopdc} (right).
There is now a clear difference between the two scenarios of
observations in line with expectations and observations in conflict.
In the prior-data conflict case, the set of posteriors (blue)
is shifted towards the left, but has about the same size as the set of priors (yellow),
and so posterior quantification of reliability has the same precision,
despite having seen two observations.
Instead, in the no conflict case, the set of posteriors is smaller than the set of priors,
such that the two observations have increased the precision of reliability statements.

@@

\newpage
\section{Robust Reliability for Complex Systems via the Survival Signature}
\label{sec:robrel}

@@

 &= { n_k - e_k \choose l_k} \int \big[P(T^k >    t \mid T^k > \tnow, \lambda_k)\big]^{l_k} \times \nonumber\\ & \hspace*{17ex}

@@

 &= { n_k - e_k \choose l_k} \int \Big[    e^{-\frac{t^{\beta_k} - (\tnow)^{\beta_k}}{\lambda_k}}\Big]^{l_k}

@@

 &= { n_k - e_k \choose l_k} \sum_{j=0}^{n_k-e_k-l_k} (-1)^j { n_k - e_k - l_k \choose j} \frac{\big(\nkn\ykn\big)^{\nkn + 1}}{\Gamma(\nkn+1)} 

@@

 &= { n_k - e_k \choose l_k} \sum_{j=0}^{n_k-e_k-l_k} (-1)^j { n_k - e_k - l_k \choose j}

>>>>

\begin{abstract}
This paper considers quantification of system reliability in scenarios
where data, that is failures or absence of failures, occurring from the 
system's use over time, are considered to be 
surprising from the perspective of prior information.
A generalized, or imprecise, Bayesian approach is presented for general
system structures, where component lifetimes have Weibull distributions with
known shape parameter. For the scale parameter, a specific set of prior distributions
is assumed which enables prior-data conflict to be reflected through increased
imprecision in posterior reliability bounds.

\end{abstract}

@@

\section{Introduction}
\label{sec:intro}
%

In this paper, we consider a system consisting of components can be divided into $K$ different groups
or types, with type $k$ components, for $k=1, \ldots, K$, assumed to have exchangeable failure
times, whilst components of different types are assumed to have independent failure times. 
We aim to predict the reliability of a running system, assuming we get component failure times 
from this system up to the moment $\tnow$ of consideration. We use the Bayesian approach for
component failure time distributions, where the ability to incorporate expert knowledge through
prior distributions is important because, for most real-world systems, one does not have 
many component failure times. In line with a generalized setting, advocated both as `robust Bayesian methods'
(\citeNP{1994:berger}) and `imprecise probability theory' (\citeNP{1991:walley,itip}),
we use a set of prior distributions which enables a level of indeterminacy to be taken into account on
the prior information, which is particularly important in practical scenarios where for example prior
knowledge may be mostly based on experience of similar but not identical components, or of such components
functioning in different systems or under different circumstances.

While the use of sets of prior distributions in Bayesian statistics has been widely presented in the
literature, the key contribution of this paper is the presentation, in the system reliability context,
of a specific set of prior distributions for the shape parameter of the Weibull distribution, such 
that conflict between prior judgements and process data on the components leads to increased imprecision
for the system reliability function, hence such conflict is explicitly reported. 
Prior-data conflict has attracted some attention in the literature (see, e.g., \citeNP{2006:evans}),
but less than one may have expected because of the obvious importance of noticing a considerable
difference between prior judgements and process data. In standard Bayesian methods, the posterior 
distribution is always effectively presenting a weighted average of the prior beliefs and the data,
without any means to show the level of disagreement between these two sources of information. It is
particularly surprising that researchers in robust Bayesian methods, who advocated the use of sets of
priors to more adequately represent lack of perfect expert knowledge, did not put more effort in study
of prior-data conflict and the possibility to use sets of prior distributions that enable such conflict
to be clearly indicated.

The approach used in this paper was introduced by \citeNP{Walter2009a} (see also \citeNP{diss} \S 3.1.4).
It proposes the use of a specific set of prior distributions leading to increased imprecision in posterior 
inferences when prior knowledge and data are in conflict than when these two sources of information are
pretty much in agreement. This paper presents the first use of this statistical method for inference on
component failure times, combined to provide predictions of a system's remaining time until failure.

While we advocate the use of a specific set of prior distributions, in a generalized Bayesian framework,
for dealing with prior-data conflict, there have also been proposals to reflect such conflict within the 
standard `precise' Bayesian approach. For example, \citeN{2008:bousquet} proposed a method for diagnostics 
of agreement or disagreement between the prior and data, based on a ratio of Kullback-Leibler divergences.
\citeN{2012:ohagan-pericchi} propose the use of heavy-tailed distributions which, in case of conflict 
between multiple sources of prior information, provide more weight to one or more of these, when combined 
with the data, than would happen with more commonly used prior distributions. Such methods 
quantify level of disagreement between prior judgements and data, yet they do not resolve the fundamental 
issue that the end result of the standard Bayesian method remains a single-valued probability
which is a weighted average of the prior and data inputs.

The paper is organized as follows. Section~\ref{sec:weibull} introduces the Bayesian model for the Weibull 
distribution with fixed shape parameter, as used later in this paper for component failure times.
Section~\ref{sec:modforsurpr} presents the use of specific sets of priors
for the scale parameter of the Weibull distribution, in order to reflect prior-data conflict.
Section~\ref{sec:robrel} presents a method to calculate system reliability bounds
for a running system based on such sets of priors. An important aspect of the presented method
is that it can be used for any system structure, through the use of the `survival signature'. 
Section~\ref{sec:elicitation} discusses elicitation of sets of prior distributions.
Section~\ref{sec:examples} contains examples illustrating the merits of our method,
by studying the effect of surprisingly early or late component failures,
showing that observations in conflict to prior assumptions
indeed lead to more cautious system reliability predictions.
Section~\ref{sec:concluding} concludes the paper by summarizing results
and discussing topics for further research.

It should be noted that this paper builds on
a paper presented at the 2015 ESREL conference and published in its proceedings \cite{2015:walter}. 
The next two sections, in which the core generalized Bayesian method for inference about component lifetimes is
introduced, follow that paper closely. Thereafter, the material presented in this paper goes far beyond
the earlier work: while before only a parallel system consisting of a single type of components was
considered, this paper presents methodology for any system structure consisting of multiple types of
components, with prior-data conflict occurring at component level yet being reflected at full system level.

@@

In this paper, we consider a system with components of $K$ different types.
There are $n_k$ components of type $k$ ($k=1,\ldots,K$) in the systems, their
failure times $T_i^k$ ($i=1,\ldots,n_k$, $k = 1, \ldots, K$) are assumed to have
a Weibull distribution with fixed shape parameter $\beta_k > 0$ and unknown scale
parameter $\lambda_k$. This distribution has the following probability density function
$f(\cdot)$ and cumulative distribution function $F(\cdot)$,
\begin{linenomath*}
\begin{align}
\label{eq:weibulldens}
f(t_i^k \mid \lambda_k) &= \frac{\beta_k}{\lambda_k} (t_i^k)^{\beta_k-1} e^{-\frac{(t_i^k)^{\beta_k}}{\lambda_k}}\,, \\
\label{eq:weibullcdf}
F(t_i^k \mid \lambda_k) &= 1 - e^{-\frac{(t_i^k)^{\beta_k}}{\lambda_k}} = P(T_i^k \leq t_i^k \mid \lambda_k)\,,
\end{align}
\end{linenomath*}
where $\lambda_k > 0$ and $t > 0$.

The shape parameter $\beta_k$ determines whether the hazard rate is constant ($\beta_k=1$), increasing ($\beta_k > 1$)
or decreasing ($\beta_k < 1$) over time. Throughout this paper we assume that $\beta_k$ is fixed, this may e.g.\ be
based on engineering knowledge and insights into the practical failure causes.
The scale parameter $\lambda_k$ can be interpreted through the relation
\begin{linenomath*}
\begin{align}
\E[T_i^k \mid \lambda_k] &= \lambda_k^{1/\beta_k}\, \Gamma(1 + 1/\beta_k)\,.
\label{eq:lambdainterpret}
\end{align}
\end{linenomath*}
where $\Gamma(\cdot)$ is the Gamma function.

In the Bayesian framework, a convenient choice of prior distribution for the scale parameter $\lambda_k$
is the inverse Gamma distribution, characterized by the probability density function (with hyperparameters 
$a_k > 0$ and $b_k > 0$)
\begin{linenomath*}
\begin{align}
f(\lambda_k\mid a_k,b_k) &= \frac{(b_k)^{a_k}}{\Gamma(a_k)} \lambda_k^{-a_k -1} e^{-\frac{b_k}{\lambda_k}}\,.
\label{eq:ig-def}
\end{align}
\end{linenomath*}
We indicate this distribution by $\lambda_k \mid a_k, b_k \sim \ig(a_k,b_k)$.
The inverse Gamma is convenient because it is a conjugate prior,
i.e., the posterior obtained by Bayes' rule is again inverse Gamma and thus easily tractable;
the prior parameters only need to be updated to obtain the posterior parameters.

For the imprecise approach presented in this paper, using a set of inverse Gamma prior distributions for $\lambda_k$,
we use a different parametrization which is more convenient to specify and interpret the set of prior distributions,
and hence also to interpret the set of corresponding posterior distributions. We use $\nz > 1$ and $\yz > 0$ instead 
of $a_k$ and $b_k$, where we drop the index $k$ for the discussion about the prior model in the following,
keeping in mind that each component type will have its own specific parameters.
Let
%\begin{linenomath*}
%\begin{align}
$\nz = a - 1$ and
%&
$\yz = b / \nz$,
%\end{align}
%\end{linenomath*}
where $\yz$ can be interpreted as the prior guess for the scale parameter $\lambda$,
as $\E[\lambda\mid\nz,\yz] = \yz$.
This parametrization also makes the nature of the combination
of prior information and data through Bayes' rule very clear:
After observing $n$ component lifetimes $\vec{t} = (t_1, \ldots, t_n)$,
the updated parameters are
\begin{linenomath*}
\begin{align}
\nn &= \nz + n\,, 
&
\yn &=  \frac{\nz \yz + \taut}{\nz + n}\,,
\label{eq:ig-update}
\end{align}
\end{linenomath*}
where $\taut = \sum_{i=1}^n (t_i)^\beta$. %
%\footnote{
Hence, the posterior distribution for $\lambda$ is
\begin{linenomath*}
\begin{align}
\lambda \mid \nz, \yz, \vec{t} \sim \ig(\nz + n + 1, \nz \yz + \taut). %}
\label{eq:ig-update-alpha}
\end{align}
\end{linenomath*}

The update rule \eqref{eq:ig-update} shows that
$\yn$ is a weighted average of the prior parameter $\yz$ and the maximum likelihood (ML) estimator $\taut/n$,
with weights proportional to $\nz$ and $n$, respectively.
This enables $\nz$ to be interpreted as a prior strength or pseudocount,
indicating how much our prior guess should weigh against the $n$ observations.
Furthermore, $\V[\lambda\mid\nz,\yz] = (\yz)^2 / (1 - 1/\nz)$,
so for fixed $\yz$, the higher $\nz$,
the more probability mass is concentrated around $\yz$. %$p(\lambda\mid\nz,\yz)$

However, the weighted average structure for $\yn$
is behind the problematic behaviour in case of prior-data conflict; we
illustrate this using a small example. Assume an expert judges that a component
has a mean lifetime of 9 weeks.
Using \eqref{eq:lambdainterpret} with $\beta=2$, we obtain $\yz = 103.13$.
We choose $\nz = 2$, so our prior guess for the mean component lifetime
counts like having two observations with this mean.
Suppose that two observations of failures of such a component become available which
are surprisingly small, say $t_1 = 1$ and $t_2 = 2$.
Using \eqref{eq:ig-update} we get $\nfun{2} = 4$
and $\yfun{2} = \frac{1}{4}(2 \cdot 103.13 + 1^2 + 2^2) = 52.82$,
so the posterior expectation for the scale parameter $\lambda$ is $52.82$,
equivalent to a mean component lifetime of $6.44$ weeks.
The posterior standard deviation (sd) for $\lambda$ is $60.99$.
Compared to the prior standard deviation of $145.85$,
the posterior expresses now more confidence that mean lifetimes are around $\yfun{2} = 52.82$
than the prior had about $\yz = 103.13$.
This irritating conclusion is illustrated in Figure~\ref{fig:weibull-pdc};
the posterior cdf is shifted halfway towards the values for $\lambda$
that the two observations suggest
(the ML estimator for $\lambda$ would be $2.5$),
and is steeper than the prior (so the pdf is more pointed),
thus conveying a false sense of certainty about $\lambda$.
We would obtain almost the same 
posterior distribution
if we had assumed the mean component lifetime to be 7 weeks (so $\yz = 62.39$),
and observed lifetimes $t_1 = 6$, $t_2 = 7$ in line with our expectations.
The main reason for developing the generalized Bayes approach with sets of priors, in order
to reflect prior-data conflict, is that it seems unreasonable to make the same probability 
statements on component lifetimes in these two fundamentally different scenarios.

@@

Despite the above mentioned issue of ignoring prior-data conflict,
the tractability of the update step
is a very attractive feature of the conjugate setting used above.
As was shown by \citeN{Walter2009a} (see also \citeNP{diss}, \S 3.1),
it is possible to retain tractability and to have a meaningful reaction to prior-data conflict
when using sets of priors generated by varying both $\nz$ and $\yz$.
Then, the magnitude of the set of posteriors,
and with it the precision of posterior probability statements,
will be sensitive to the degree of prior-data conflict,
leading to more cautious probability statements when prior-data conflict occurs.

The generalized Bayes approach for the model for a component's lifetime in this
paper is as follows. Instead of a single prior guess $\yz$ for the mean component 
lifetimes, a range of prior guesses $[\yzl, \yzu]$ is used, together with a range $[\nzl, \nzu]$ of pseudocounts.
The set of prior distributions considered is therefore
\begin{linenomath*}
\begin{align}
\MZ := \{ f(\lambda\mid\nz,\yz) \mid \nz \in [\nzl, \nzu], \yz \in [\yzl, \yzu] \}
\label{eq:setofpriors}
\end{align}
\end{linenomath*}
Each of the priors $f(\lambda\mid\nz,\yz)$ is then updated to the posterior
$f(\lambda\mid\nz,\yz,\vec{t}) = f(\lambda\mid\nn,\yn)$
by using \eqref{eq:ig-update},
such that the set of posteriors $\MN$ becomes
$\MN = \{ f(\lambda\mid\nn,\yn) \mid \nz \in [\nzl, \nzu], \yz \in [\yzl, \yzu] \}$.
This procedure of using Bayes' Rule element by element
is seen as self-evident in the robust Bayesian literature,
but can be formally justified as being \emph{coherent}
(a self-consistency property)
in the framework of imprecise probability, where it is known as
\emph{Generalized Bayes' Rule} \cite[\S 6.4]{1991:walley}.

In order to reflect possible prior-data conflict, it is crucial to consider a range of pseudocounts $[\nzl, \nzu]$
along with the range of prior guesses $[\yzl, \yzu]$, as only in this case $\taut/n \not\in [\yzl, \yzu]$
leads to the set of posteriors being larger and hence reflecting prior-data conflict, as will be illustrated below and
in the subsequent sections.

Continuing the example from Section~\ref{sec:weibull} and Figure~\ref{fig:weibull-pdc},
assume now for the mean component lifetimes the range 9 to 11 weeks,
this corresponds to $[\yzl,\yzu] = [103.13, 154.06]$.
Choosing $[\nzl,\nzu] =[2, 5]$
means that this information on the mean component lifetimes is considered to be of equivalent value to having to two to five 
actual observations.
Compare now the set of posteriors obtained from observing
$t_1 = 1$, $t_2 = 2$ (as before), see Figure~\ref{fig:setofpost-pdc-nopdc} (left),
and $t_1 = 10$, $t_2 = 11$, see Figure~\ref{fig:setofpost-pdc-nopdc} (right).
There is now a clear difference between the two scenarios of
observations in line with expectations and observations in conflict.
In the prior-data conflict case, the set of posteriors (blue)
is shifted towards the left, but has about the same size as the set of priors (yellow),
and so posterior quantification of reliability has the same precision,
despite having seen two observations.
Instead, in the no conflict case, the set of posteriors is smaller than the set of priors,
such that the two observations have increased the precision of reliability statements.

@@

\section{Robust Reliability for Complex Systems via the Survival Signature}
\label{sec:robrel}

@@

 &= \binom{n_k - e_k}{l_k} \int \big[P(T^k >    t \mid T^k > \tnow, \lambda_k)\big]^{l_k} \times \nonumber\\ & \hspace*{17ex}

@@

 &= \binom{n_k - e_k}{l_k} \int \Big[    e^{-\frac{t^{\beta_k} - (\tnow)^{\beta_k}}{\lambda_k}}\Big]^{l_k}

@@

 &= \binom{n_k - e_k}{l_k} \sum_{j=0}^{n_k-e_k-l_k} (-1)^j \binom{n_k - e_k - l_k}{j} \frac{\big(\nkn\ykn\big)^{\nkn + 1}}{\Gamma(\nkn+1)} 

@@

 &= \binom{n_k - e_k}{l_k} \sum_{j=0}^{n_k-e_k-l_k} (-1)^j \binom{n_k - e_k - l_k}{j}
